Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool

### 2020-06-22 article.Rmd

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Malcolm Morgan, Joey Talbot, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
output:
  bookdown::pdf_document2:
    keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---

>>>>

---
title: "Methods to prioritise pop-up active transport infrastructure and their application in a national cycleway prioritisation tool"
# : overview and findings from 10 UK cities"
author: "Robin Lovelace, Joey Talbot, Malcolm Morgan, Martin-Lucas-Smith"
# output: bookdown::github_document2
# output: bookdown::html_document2
output:
  bookdown::pdf_document2:
    keep_tex: true
# bibliography: references.bib
bibliography: refs.bib
---
